\Huge Don't interpolate the data!

### 2023-09-21 paper/main.tex

@@

We assumed no sky subtraction necessary. No tellurics. What gives if you have multiple shifting signals. Causal structure. etc.

What about non-Gaussian noise?

Code is available at HOGG THIS URL.

>>>>

% Hogg's email epiphany:
% 1. I think I figured out what Blanton means by saying that interpolation of the data is a kind of fitting. It is! But those fits can’t be combined well because the fits are infinitely over-parameterized. If the interpolation was done approximately with a finite-parameter fit, we could interpolate and then average just fine. I’m writing this here to remind myself of this epiphany for when I come back online and write a subsection about this in the paper.

% Hogg: what do you want to do about this?

@@

% What about non-Gaussian noise?

We assumed that the noise was Gaussian, but this is not always true of astronomical data.
In the case of Poisson noise that is not background dominated, the variance tensor $C_i$ will be biased, and all our assumptions about additive Gaussian variance will be broken. % ARC: what else should we say about this?

Code is available at \url{https://github.com/davidwhogg/NoDataInterpolation} and is registered in the Python Package Index as \texttt{NoDataInterpolation}.
